\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
	\item Two dice are thrown together. Find the probability that the product of the numbers
on the top of the dice is
\begin{enumerate}
\item 6
\item 12
\item 7
\end{enumerate}
		\solution
		\input{exemplar/10/13/3/21/main.tex}
		%
  \item Two dice are thrown simultaneously. What is the probability that the sum of the numbers appearing on the dice is 
\begin{enumerate}
\item{7?}
\item{a prime number?}
\item{1?}
\end{enumerate}
\solution
\input{exemplar/10/13/3/20/q20.tex}
\item Two dice are thrown at the same time. Find the probability of getting
\begin{enumerate}
    \item[(i)] same number on both dice.
    \item[(ii)] different numbers on both dice.
\end{enumerate}
\input{exemplar/10/13/3/19/main.tex}
\item A die has its face marked 0,1,1,1,6,6. Two such dice are thrown together and their score is recorded.
\begin{enumerate}
	\item How many different scores are possible ?
	\item What is the probability of getting a total 7 ?  
\end{enumerate}
\input{exemplar/10/13/3/39/main.tex}
\item For a loaded die, the probabilities of outcomes are given as under:
$\Pr(1) = \Pr(2) = 0.2, \Pr(3) = \Pr(5) = \Pr(6) = 0.1$ and $\Pr(4) = 0.3$
The die is thrown two times. Let A and B be the events, 'same number each time', and
'a total score is 10 or more' ,respectively. Determine whether or not A and B are independent.
\input{exemplar/12/13/3/1/main.tex}
\item Three dice are thrown at the sametime. Find the probability of getting three
two’s, if it is known that the sum of the numbers on the dice was six.
\input{exemplar/12/13/3/14/main2.tex}
\item Two dice are tossed. Find whether the following two events A and B are independent:\\
A = \{(x,y) : x+y=11\} B = \{(x,y): x $\neq$ 5\}\\
where (x,y) denotes a typical sample point.
\input{exemplar/12/13/3/39/main.tex}
\item Find the probability distribution of the maximum of the two scores obtained when a die is thrown twice. Determine also the mean of the distribution.\\
\input{exemplar/12/13/3/35/main.tex}
\item Two dice are thrown. If it is known that sum of the numbers on the dice was less than 6,the probability of getting a sum 3, is
\begin{enumerate}[label=\Alph*)]
\item $\frac{1}{18}$ \\
\item $\frac{5}{18}$ \\
\item $\frac{1}{5}$ \\
\item $\frac{2}{5}$ 
\end{enumerate}
\input{exemplar/12/13/3/82/main.tex}
\item Two dice are thrown at the same time. Determine the probabiity that the difference
of the numbers on the two dice is 2. \\
\input{exemplar/10/13/3/26/main.tex}
\end{enumerate}
