\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
	\item  A die is loaded in such a way that each odd number is twice as likely to occur as
each even number. Find $P(G)$, where $G$ is the event that a number greater than
3 occurs on a single roll of the die.
\\
\solution
		\input{exemplar/11/16/3/5/main.tex}
	\item All the jacks, queens and kings are removed from a deck of 52 playing cards. The remaining cards are well shuffled and then one card is drawn at random. Giving ace a value 1 similar value for other cards, find the probability that the card has a value 
		\begin{enumerate}
			\item 7
			\item greater than 7
			\item less than 7
		\end{enumerate}
		\input{exemplar/10/13/3/30/main.tex}
  \item A Lot consists of 48 mobile phones of which 42 are good, 3 have only minor defects and 3 have major defects.Varnika will buy a phone if it is good but the trader will only buy a mobile if it has no major defects. One phone is selected at random from the lot. What is the probability that it is
\begin{enumerate}
	\item acceptable to Varnika?
            \item acceptable to the trader?
\end{enumerate}
\solution
	\input{exemplar/10/13/3/40/main.tex}
 \item A student says that if you throw a die, it will show up 1 or not 1. Therefore, the probability of getting 1 and the probability of getting 'not 1' each is equal to $\frac{1}{2}$. Is this correct? Give reasons.\\
 \solution
        \input{exemplar/10/13/2/9/main.tex}
   \item Four candidates A, B, C, D have ap-
plied for the assignment to coach a school cricket
team. If A is twice as likely to be selected as B, and
B and C are given about the same chance of being
selected, while C is twice as likely to be selected
as D, what are the probabilities that
\begin{enumerate}
\item C will be selected?
\item A will not be selected?
\end{enumerate}
	\input{exemplar/11/16/3/9/main.tex}
 \item A bag contain 24 balls of which $x$ balls are red, $2x$ are white and $3x$ are blue. A ball is selected at random, What is the probability that it is
\begin{enumerate}[label=\alph*)]
\item not red ?
\item white ?
\end{enumerate}
\input{exemplar/10/13/3/41/main.tex}
If the letters of the word ASSASSINATION are arranged at random. Find the Probability that
\begin{enumerate}[label=(\alph*)]
\item Four $S's$ come consecutively in the word
\item Two  $I's$ and two $N's$ come together
\item All $A's$ are not coming together
\item No two $A's$ are coming together
\end{enumerate}
\input{exemplar/11/16/3/14/main.tex}
\end{enumerate}
