\begin{enumerate}[label=\thechapter.\arabic*,ref=\thechapter.\theenumi]
	\item 
Given that E and F are events such that $P(E)=0.6, P(F)=0.3$ and $P(E F)=0.2$, find $P(E \mid F)$ and $P(F \mid E)$.
\\
\input{ncert/12/13/1/1/cond.tex}
	\item Compute $\pr{A|B}$, if $\pr{B}=0.5$ and $\pr{AB}=0.32$. 
		\\
	\item Probability that A speaks truth is
$\frac{4}{5}$ . A coin is tossed. A reports that a head
appears. The probability that actually there was head is
\begin{enumerate}
    \item $\frac{4}{5}$ 
\item $\frac{1}{2}$ 
\item $\frac{1}{5}$ 
\item $\frac{2}{5}$
\end{enumerate}
	\item Compute $\pr{A|B}$, if $\pr{B}=0.5$ and $\pr{AB}=0.32$. 
		\\
		\input{ncert/12/13/1/2/cond.tex}

	\item If $\pr{A}$ = 0.8, $\pr{B} = 0.5$ and $\pr{B \vert A = 0.4}$, find  
\begin{enumerate}
\item
$\pr{AB}$ 
\item
 $\pr{A \vert B}$
\item
 $\pr{A+B}$
\end{enumerate}
\solution
%\input{ncert/12/13/1/3/axioms.tex}
\iffalse
	\item If $\pr{A}=\frac{6}{11}$, $\pr{B}=\frac{5}{11}$ and $\pr{A+B}=\frac{7}{11}$, find
\begin{enumerate}
	\item $\pr{AB}$   
	\item $\pr{A \mid B}$
	\item $\pr{B \mid A}$
\end{enumerate}
\solution
		\input{ncert/12/13/1/5/axioms.tex}
\fi
\item Mother, Father and Son line up at random for a family picture. Determine \pr{E \mid F} where 
$E$: Son on one end, $F$: Father in middle\\
\solution
		\input{ncert/12/13/1/9/cond.tex}
	\item Assume that each born child is equally likely to be a boy or a girl. If a family has
two children, what is the conditional probability that both are girls given that
\begin{enumerate}
	\item  The youngest is a girl
	\item  At least one is a girl
\end{enumerate}
\solution
		\input{ncert/12/13/1/12/main.tex}
	\item An instructor has a question bank consisting of 300 easy True / False questions,
200 difficult True / False questions, 500 easy multiple choice questions and 400
difficult multiple choice questions. If a question is selected at random from the
question bank, what is the probability that it will be an easy question given that it
is a multiple choice question?
\\
\solution
		\input{ncert/12/13/1/13/main.tex}
\item If $ \pr{A}  = \frac{1}{2}$, $\pr{B} = 0$, then $\pr{A \mid B}$ is
\begin{enumerate}
\item 0
\item $\frac{1}{2}$
\item not defined
\item 1
\end{enumerate}
	\input{ncert/12/13/1/16/cond.tex}
 \item If $A$ and $B$ are events such that 
    \begin{align}
        \pr{A|B} = \pr{B|A}
        \label{eq:ncert/12/13/1/17/cond}
    \end{align} 
    then 
    \begin{enumerate}
        \item $A \subset B$ but $A \neq B$
        \item $A = B$ 
        \item $A \cap B = \phi$ 
        \item $\pr{A} = \pr{B}$
    \end{enumerate}
    \solution
\input{ncert/12/13/1/17/axioms.tex}
 \item Consider the experiment of throwing a die, if a multiple of 3 comes up, 
    throw the die again and if any other number comes, toss a coin. Find the 
    conditional probability of the event `the coin shows a tail', given that `at 
    least one die shows a 3'.
\\
\solution
\input{ncert/12/13/1/15/cond.tex}
%
\item Two cards are drawn at random and without replacement from a pack of 52 playing cards. Find the probability that both the cards are black.\\
\solution
\input{ncert/12/13/2/2/cond.tex}
%
\item Let $A$ and $B$ be independent events with $P(A)=0.3$ and $P(B)=0.4$. Find
		\label{ncert/12/13/2/7}
\begin{enumerate}
\item $P(A \cap B)$
\item $P(A \cup B)$
\item $P(A|B)$
\item $P(B|A)$
\end{enumerate}
%
\item An urn contains 5 red and 5 black balls. A ball is drawn at random, its colour is
noted and is returned to the urn. Moreover, 2 additional balls of the colour drawn
are put in the urn and then a ball is drawn at random. What is the probability that
the second ball is red?
		\label{ncert/12/13/3/1}
\\
\solution
\input{ncert/12/13/3/1/cond.tex}
\item A bag contains 4 red and 4 black balls, another bag contains 2 red and 6 black
balls. One of the two bags is selected at random and a ball is drawn from the bag
which is found to be red. Find the probability that the ball is drawn from the
first bag.
		\label{ncert/12/13/3/2}
\item Of the students in a college, it is known that 60\% reside in hostel and 40\% are
day scholars (not residing in hostel). Previous year results report that 30\% of all
students who reside in hostel attain A grade and 20\% of day scholars attain A
grade in their annual examination. At the end of the year, one student is chosen
at random from the college and he has an A grade, what is the probability that the
student is a hostlier?     
		\label{ncert/12/13/3/3}
\\
\solution
\input{ncert/12/13/3/3/main.tex}
\item In answering a question on a multiple choice test, a student either knows the
answer or guesses. Let
$\frac{3}{4}$ be the probability that he knows the answer and
$\frac{1}{4}$
be the probability that he guesses. Assuming that a student who guesses at the
answer will be correct with probability
$\frac{1}{4}$. What is the probability that the student knows the answer given that he answered it correctly?
\\
\solution
\input{ncert/12/13/3/4/cond.tex}
\item A laboratory blood test is 99\% effective in detecting a certain disease when it is
in fact, present. However, the test also yields a false positive result for 0.5\% of
the healthy person tested (i.e. if a healthy person is tested, then, with probability
0.005, the test will imply he has the disease). If 0.1 percent of the population
actually has the disease, what is the probability that a person has the disease
given that his test result is positive ?
\\
\solution
\input{ncert/12/13/3/5/main.tex}
\item There are three coins. One is a two headed coin (having head on both faces),
another is a biased coin that comes up heads 75\% of the time and third is an
unbiased coin. One of the three coins is chosen at random and tossed, it shows
heads, what is the probability that it was the two headed coin ?
\\
\solution
\input{ncert/12/13/3/6/cond.tex}

\item An insurance company insured 2000 scooter drivers, 4000 car drivers and 6000
truck drivers. The probability of an accidents are 0.01, 0.03 and 0.15 respectively.
One of the insured persons meets with an accident. What is the probability that
he is a scooter driver?
\item A factory has two machines A and B. Past record shows that machine A produced
60\% of the items of output and machine B produced 40\% of the items. Further,
2\% of the items produced by machine A and 1\% produced by machine B were
defective. All the items are put into one stockpile and then one item is chosen at
random from this and is found to be defective. What is the probability that it was
produced by machine B?

\item. Two groups are competing for the position on the Board of directors of a
corporation. The probabilities that the first and the second groups will win are
0.6 and 0.4 respectively. Further, if the first group wins, the probability of
introducing a new product is 0.7 and the corresponding prbability is 0.3 if the
second group wins. Find the probability that the new product introduced was by
the second group.
\\
\solution
\input{ncert/12/13/3/9/cond.tex}
\item Suppose a girl throws a die. If she gets a 5 or 6, she tosses a coin three times and
notes the number of heads. If she gets 1, 2, 3 or 4, she tosses a coin once and
notes whether a head or tail is obtained. If she obtained exactly one head, what
is the probability that she threw 1, 2, 3 or 4 with the die?]
\item A manufacturer has three machine operators A, B and C. The first operator A
produces 1\% defective items, where as the other two operators B and C produce 5\% and 7\% defective items respectively. A is on the job for 50\% of the
time, B is on the job for 30\% of the time and C is on the job for 20\% of the time.
A defective item is produced, what is the probability that it was produced by A?
\item A card from a pack of 52 cards is lost. From the remaining cards of the pack,
two cards are drawn and are found to be both diamonds. Find the probability of
the lost card being a diamond.
%
\item Probability that A speaks truth is
$\frac{4}{5}$. A coin is tossed. A reports that a head
appears. The probability that actually there was head is
\begin{enumerate}
\item $\frac{4}{5}$ 
\item $\frac{1}{2}$ 
\item $\frac{1}{5}$ 
\item $\frac{2}{5}$
\end{enumerate}
\solution
\input{ncert/12/13/3/13/cond.tex}
\item 
		If $A$ and $B$ are two events such that $A \subset B$ and $\pr{B} \neq 0$, then which of the following is correct ?
\begin{enumerate}
\item $\pr{A \mid B} = \frac{\pr{B}}{\pr{A}}$ 
\item $\pr{A \mid B} < \pr{A}$
\item $\pr{A \mid B} \geq \pr{A}$  
\item None of these
\end{enumerate}
\solution
\input{ncert/12/13/3/14/axioms.tex}
\item $A$ and $B$ are two events such that $\pr{A} \neq 0$. Find $\pr{B \mid A}$, if
\begin{enumerate}
\item $A$ is a subset of $B$
\item $A \cap B = \phi$
\end{enumerate}
\solution 
	\input{ncert/12/13/6/1/cond.tex}
	%
\item A couple has two children.
\begin{enumerate}
\item Find the probability that both children are males, if it is known that at least one of the children is male.
\item Find the probability that both children are females, if it is known that the elder child is a female.
\end{enumerate}
\solution 
	\input{ncert/12/13/6/2/cond.tex}
	\item Suppose that $5\%$ of men and $0.25\%$ of women have grey hair. A grey haired person is selected at random. What is the probability that this person being male? Assume that there are equal number of males and females.
\\
\solution
		\input{ncert/12/13/6/3/main.tex}
\item Suppose we have four boxes A,B,C and D containing coloured marbles as given in \tabref{tab:12/13/6/12/table1}. 
\begin{table}[htbp]
\centering
\input{ncert/12/13/6/12/tables/question_table.tex}
\caption{Question Table}
\label{tab:12/13/6/12/table1}
\end{table}
One of the boxes has been selected at random and a single marble is drawn from it.$\,$If the marble is red,$\,$what is the probability that it was drawn from \\1) Box A ?\\2) Box B ?\\3) Box C ?
\\
\solution 
	\input{ncert/12/13/6/12/main.tex}
\item Bag I contains 3 red and 4 black balls and Bag II contains 4 red and 5 black balls.
One ball is transferred from Bag I to Bag II and then a ball is drawn from Bag II.
The ball so drawn is found to be red in colour. Find the probability that the
transferred ball is black. 
\\
\solution
		\input{ncert/12/13/6/16/main.tex}
\item Box A contains 25 slips of which 19 are marked Rs 1 and others are marked Rs 5 each. Box B contains 50 slips of which 45 are marked Rs 1 and others are marked Rs 13 each. Slips of both boxes are poured into a third box and reshuffled. A slip is drawn at random. What is the probability that it is marked other than Rs 1?\\
\solution
\input{exemplar/10/13/3/35/main.tex}
\item Bag I contains 3 black and 2 white balls, Bag II contains 2 black and 4 white
balls. A bag and a ball is selected at random. Determine the probability of selecting
a black ball.\\
\solution
\input{exemplar/12/13/3/17/main.tex}
\item While shuffling a pack of 52 playing cards, 2 cards are dropped. Find the probabilty that the missing cards to be of different colours.\\
\solution
\input{exemplar/11/16/3/20/main.tex}
\item A bag contains $(2n + 1)$ coins. It is known that n of these coins have a head on
both sides where as the rest of the coins are fair. A coin is picked up at random
from the bag and is tossed. If the probability that the toss results in a head is $\frac{31}{42}$
, determine the value of $n$.\\
\solution
\input{exemplar/12/13/3/52/main.tex}
\item An urn contains $m$ white and $n$ black balls. A ball is drawn at random and is put
back into the urn along with $k$ additional balls of the same colour as that of the
ball drawn. A ball is again drawn at random. Show that the probability of
drawing a white ball now does not depend on $k$.\\
\solution
\input{exemplar/12/13/3/40/main.tex}
\item If $\pr{AB}=\frac{7}{10}$ and $\pr{B}=\frac{17}{20}$, then $\pr{A|B}$ equals
\begin{enumerate}
\item $\frac{14}{17}$
\item $\frac{17}{20}$
\item $\frac{7}{8}$
\item $\frac{1}{8}$
\end{enumerate}
\input{exemplar/12/13/3/57/main.tex}
\item 
A letter is known to have come either from TATANAGAR or from CALCUTTA. On the envelope, just two consecutive letter TA are visible. What is the probability that the letter came from TATANAGAR.\\
\solution
\input{exemplar/12/13/3/44/main.tex}
\item A bag contain (2n+1) coins. It is known that n of these coins have a head on both sides where as the rest of the coins are fair. A coin is picked up at random from the bag and is tossed. If the probability that the toss results in a head is $\frac{31}{42}$, determine the value of n.
\input{exemplar/12/13/3/52a/main.tex}
\item By examining the chest X ray, the probability that TB is detected when a person
is actually suffering is 0.99. The probability of an healthy person diagnosed to 
have TB is 0.001. In a certain city, 1 in 1000 people suffers from TB. A person
is selected at random and is diagnosed to have TB. What is the probability that
he actually has TB? \\
\input{exemplar/12/13/3/47/main.tex}
\end{enumerate}

