\begin{enumerate}[label=\thechapter.\arabic*,ref=\thechapter.\theenumi]
	\item A lot consists of 144 ball pens of which 20 are defective and the 
    others are good. Nuri will buy a pen if it is good, but will not buy if it 
    is defective. The shopkeeper draws one pen at random and gives it to her. 
    What is the probability that
    \begin{enumerate}
        \item She will buy it?
        \item She will not buy it?
    \end{enumerate}
\solution
\input{ncert/10/5/1/21/bernoulli.tex}
\item A box contains 5 red marbles, 8 white marbles and 4 green marbles.One marble is taken
out of the box at random. What is the probability that the marble taken out will be 
\\
\solution
\begin{enumerate}
    \item red ? 
    \item white ? 
    \item  not green?
\end{enumerate}
\input{ncert/10/15/1/9/multinom.tex}

\item A die is thrown, find the probability of following events:
\begin{enumerate}
\item A prime number will appear
\item A number greater than or equal to 3 will appear
\item A number less than or equal to one will appear
\item A number more than 6 will appear
\item A number less than 6 will appear
\end{enumerate}
\solution
\input{ncert/11/16/3/3/bernoulli.tex}
  \item Three coins are tossed once. Find the probability of getting 
    \begin{enumerate}
        \item 3 heads
        \item 2 heads
        \item atleast 2 heads 
        \item atmost 2 heads
        \item no head
        \item 3 tails 
        \item exactly two tails
        \item no tail
        \item atmost two tails
    \end{enumerate}
\solution
\input{ncert/11/16/3/8/binom.tex}
	\item Two dice, one blue and one grey, are thrown at the same time.   The event defined by the sum of the two numbers appearing on the top of the dice can have 11 possible outcomes 2, 3, 4, 5, 6, 6, 8, 9, 10, 11 and 12.  A student argues that each of these outcomes has a probability $\frac{1}{11}$.  Do you agree with this argument?  Justify your answer.
		%
\item A box contains 10 red marbles, 20 blue marbles and 30 green marbles. 5 marbles
are drawn from the box, what is the probability that
\begin{enumerate}
\item all will be blue?
\item atleast one will be green?
\end{enumerate}
\solution
\input{ncert/11/16/4/1/multinom.tex}
	\item 
	A game consists of tossing a one rupee coin 3 times and noting its outcome each time. Hanif wins if all the tosses give the same result i.e., three heads or three tails, and loses otherwise. Calculate the probability that Hanif will lose the game
\\
%\input{ncert/12/13/1/1/cond.tex}
\item A coin is tossed three times, where. Determine \pr{E \mid F} where
\begin{enumerate}
\item $E$ : head on third toss, $F$ : heads on first two tosses
\item $E$ : at least two heads, $F$ : at most two heads
\item $E$ : at most two tails, $F$ : at least one tail
\end{enumerate}
\solution 
\input{ncert/12/13/1/6/cond.tex}
\item A box of oranges is inspected by examining three randomly selected oranges drawn without replacement. If all the three oranges are good, the box is approved for sale, otherwise, it is rejected. Find the probability that a box containing 15 oranges out of which 12 are good and 3 are bad ones will be approved for sale.\\
	\solution
\input{ncert/12/13/2/3/multinom.tex}
\item A die is tossed thrice. Find the probability of getting an odd number at least once.
		\label{ncert/12/13/2/11}
\item Find the probability distribution of
\begin{enumerate}
	\item number of heads in two tosses of a coin.
	\item number of tails in the simultaneous tosses of three coins.
	\item number of heads in four tosses of a coin.
\end{enumerate}
\solution
\input{ncert/12/13/4/4/dist.tex}
\item  The random variable $X$ has a probability distribution \pr{X} of the following form, where $k$ is some number 
\begin{align}
  \pr{X} =
    \begin{cases}
      k,  & x=0\\
      2k, & x=1\\
      3k, & x=2\\
      0 , & \text{otherwise}
    \end{cases}       
\end{align}
		\begin{enumerate}
			\item
 Determine the value of $k$ 

\item  Find \pr{X < 2},\pr{X \leq 2},\pr{X \geq 2}  
		\end{enumerate}
\solution
\input{ncert/12/13/4/9/dist.tex}
\item 
Find the mean number of heads in three tosses of a fair coin.
\\
\solution
\input{ncert/12/13/4/10/binom.tex}
\item State which of the following are not the probability distributions of a random 
variable. Give reasons for your answer
\renewcommand{\labelenumii}{\roman{enumii}}
\begin{enumerate}

\item \begin{table}[ht!]\centering
\input{ncert/13/4/tables/Book.tex}
\end{table}

\item \begin{table}[ht!]\centering
\input{ncert/13/4/tables/Book2.tex}
\end{table}

\item  \begin{table}[ht!]\centering
\input{ncert/13/4/tables/Book3.tex}	
\end{table}

\item  \begin{table}[ht!]\centering
\input{ncert/13/4/tables/Book5.tex}	
\end{table} 


\end{enumerate}
\item There are 5\% defective items in a large bulk of items. What is the probability that a sample of 10 items will include not more than one defective item?
	\\
\solution
\input{ncert/12/13/5/3/binom.tex}
\item Five cards are drawn successively with replacement from a well-shuffled deck
of 52 cards. What is the probability that
\begin{enumerate}
    \item all the five cards are spades?
    \item only 3 cards are spades?
    \item none is a spade?
\end{enumerate}
\solution
\input{ncert/12/13/5/4/binom.tex}
\item The probability that a bulb produced by a factory will fuse after 150 days of use
is $0.05$. Find the probability that out of 5 such bulbs
\begin{enumerate}
\item  none
\item not more than one
\item more than one
\item at least one
\end{enumerate}
will fuse after 150 days of use.
\\
\solution
\input{ncert/12/13/5/5/binom.tex}
  \item An urn contains 25 balls of which 10 balls bear a mark `X' and the 
    remaining 15 bear a mark `Y'. A ball is drawn at random from the urn, its 
    mark is noted down and it is replaced. If 6 balls are drawn in this way, 
    find the probability that 
    \begin{enumerate}
        \item all will bear `X' mark. 
        \item not more than 2 will bear `Y' mark. 
        \item at least one ball will bear `Y' mark. 
        \item the number of balls with `X' mark and `Y' mark will be equal.
    \end{enumerate}
\solution
\input{ncert/12/13/6/5/binom.tex}

\item An urn contains 5 red and 2 black balls. Two balls are randomly drawn. Let X
represent the number of black balls. What are the possible values of X? Is X a
random variable ? 
\
\item Let X represent the difference between the number of heads and the number of
tails obtained when a coin is tossed 6 times. What are possible values of X?

\item Find the probability distribution of
\begin{enumerate}
\item number of heads in two tosses of a coin.
\item number of tails in the simultaneous tosses of three coins.
\item number of heads in four tosses of a coin.
\end{enumerate}

\item Find the probability distribution of the number of successes in two tosses of a die,
where a success is defined as
\begin{enumerate}
\item number greater than 4
\item six appears on at least one die
\end{enumerate}
 

\item From a lot of 30 bulbs which include 6 defectives, a sample of 4 bulbs is drawn
at random with replacement. Find the probability distribution of the number of
defective bulbs.

\item A coin is biased so that the head is 3 times as likely to occur as tail. If the coin is
tossed twice, find the probability distribution of number of tails.
\item A coin is tossed twice, what is the probability that atleast one tail occurs?
\\
\solution
\input{ncert/11/16/3/2/binom.tex}
\item A random variable X has the following probability distribution\\

Determine

\begin{enumerate}
\begin{table}[ht!]\centering
\input{ncert/13/4/tables/Book10.tex}
\end{table}
\item k
\item P$(X < 3)$
\item P$(X > 6)$
\item P$(0 < X < 3)$

\end{enumerate}

\item The random variable X has a probability distribution P(X) of the following form,
where k is some number :
\[P(x)=\begin{cases}
k, & \mbox{if}\; x= 0\\
2k, & \mbox{if}\; x= 1\\
3k, & \mbox{if}\; x= 2\\
0, & otherwise
\end{cases}\]
\begin{enumerate}
\item Determine the value of k.
\item Find P $(X < 2)$, P $(X \leq 2)$, P$(X \geq 2)$
\end{enumerate}
\item Find the mean number of heads in three tosses of a fair coin.

\item Two dice are thrown simultaneously. If X denotes the number of sixes, find the
expectation of X.

\item Two numbers are selected at random (without replacement) from the first six
positive integers. Let X denote the larger of the two numbers obtained. Find
E(X).

\item Let X denote the sum of the numbers obtained when two fair dice are rolled.
Find the variance and standard deviation of X.

\item A class has 15 students whose ages are 14, 17, 15, 14, 21, 17, 19, 20, 16, 18, 20,
17, 16, 19 and 20 years. One student is selected in such a manner that each has
the same chance of being chosen and the age X of the selected student is
recorded. What is the probability distribution of the random variable X? Find
mean, variance and standard deviation of X.

\item In a meeting, 70% of the members favour and 30% oppose a certain proposal.
A member is selected at random and we take X = 0 if he opposed, and X = 1 if
he is in favour. Find E(X) and Var (X).\\

Choose the correct answer in each of the following:



\item The mean of the numbers obtained on throwing a die having written 1 on three
faces, 2 on two faces and 5 on one face is
\begin{enumerate}
\item 1
\item 2
\item 5
\item $\frac{8}{3}$

\end{enumerate}

\item Suppose that two cards are drawn at random from a deck of cards. Let X be the
number of aces obtained. Then the value of E(X) is
\begin{enumerate}

\item $\frac{37}{221}$
\item $\frac{5}{13}$
\item $\frac{1}{13}$
\item $\frac{2}{13}$

\end{enumerate}

\end{enumerate}
