%\begin{enumerate}[label=\thechapter.\arabic*,ref=\thechapter.\theenumi]
\item Suppose that 90 \% of people are right-handed. What is the probability that atmost 6 of a random sample of 10 people are right-handed. 
	\\
\solution
\input{ncert/12/13/6/4/gauss.tex}
\item There are 5\% defective items in a large bulk of items. What is the probability that a sample of 10 items will include not more than one defective item?
	\\
\solution
\input{ncert/9/3/2/main.tex}
\item Five cards are drawn successively with replacement from a well-shuffled deck
of 52 cards. What is the probability that
\begin{enumerate}
    \item all the five cards are spades?
    \item only 3 cards are spades?
    \item none is a spade?
\end{enumerate}
\solution
\\
\input{ncert/9/3/3/main.tex}
\item In an examination, 20 questions of true-false type are asked. Suppose a student tosses a fair coin to determine his answer to each question. If the coin falls heads, he answer true; if it falls tails, he answer false. Find the probability that he answers at least 12 questions correctly.\\
\\
\solution
\input{ncert/9/3/4/main.tex}
\item It is known that 10 $\%$ of certain articles manufactured are defective. What is the probability that in a random sample space of 12 such articles,9 are defective? \\
\solution
\input{ncert/9/3/5/main.tex}
\item The probability that a student is not a swimmer is $\frac{1}{5}$ .Then the probability that out of five students, four are swimmers 
\begin{enumerate}
    \item $\comb{5}{4}\brak{\frac{4}{5}}^{4}\frac{1}{5}$ \label{item:9.3.6/1} \\
    \item $\brak{\frac{4}{5}}^{4}\frac{1}{5}$ \label{item:9.3.6/2} \\
    \item \label{item:9.3.6/3}$\comb{5}{1}\frac{1}{5}\brak{\frac{4}{5}}^{4}$\\
    \item \label{item:9.3.6/4}None of these
\end{enumerate}
\solution
\input{ncert/9/3/6/main.tex}
\item There are 5\% defective items in a large bulk of items. What is the probability that a sample of 10 items will include not more than one defective item?
	\\
\solution
\input{ncert/9/3/7/main.tex}
\item Five cards are drawn successively with replacement from a well-shuffled deck
of 52 cards. What is the probability that
\begin{enumerate}
    \item all the five cards are spades?
    \item only 3 cards are spades?
    \item none is a spade?
\end{enumerate}
\solution
\input{ncert/9/3/8/main.tex}
\item The probability that a bulb produced by a factory will fuse after 150 days of use
is $0.05$. Find the probability that out of 5 such bulbs
\begin{enumerate}
\item  none
\item not more than one
\item more than one
\item at least one
\end{enumerate}
will fuse after 150 days of use.
\\
\input{ncert/9/3/9/main.tex}
\item A bag consists of 10 balls each marked with one of the digits 0 to 9. If 4 balls are drawn successively with replacement from the bag, what is the probability that none is marked with the digit 0?
\\
\solution
\input{ncert/9/3/10/main.tex}
\item How many times must a man toss a fair coin so that the probability of having at least one head is more than 90\%?
\\
\input{ncert/9/3/11/main.tex}
\item In an examination, 20 questions of true-false type are asked. Suppose a student tosses a fair coin to determine his answer to each question. If the coin falls heads, he answer true; if it falls tails, he answer false. Find the probability that he answers at least 12 questions correctly.\\
\solution
\input{ncert/9/3/12/main.tex}
\item Find the probability of getting 5 twice in 7 throws of a dice.\\
\solution\\
\input{ncert/9/3/13/prob.tex}
\item On a multiple choice examination with three possible answers for each of the five questions, what is the probability that a candidate would get four or more correct answers just by guessing$?$
\\
\input{ncert/9/3/14/main.tex}
\item Find the probability of throwing at most 2 sixes in 6 throws of a single die.\\
\solution
\item Suppose that 90 \% of people are right-handed. What is the probability that atmost 6 of a random sample of 10 people are right-handed. 
\\
\solution
\input{ncert/9/3/16/main.tex}
  \item An urn contains 25 balls of which 10 balls bear a mark `X' and the 
    remaining 15 bear a mark `Y'. A ball is drawn at random from the urn, its 
    mark is noted down and it is replaced. If 6 balls are drawn in this way, 
    find the probability that 
    \begin{enumerate}
        \item all will bear `X' mark. 
        \item not more than 2 will bear `Y' mark. 
        \item at least one ball will bear `Y' mark. 
        \item the number of balls with `X' mark and `Y' mark will be equal.
    \end{enumerate}
\solution
\input{ncert/9/3/17/main.tex}
\item From a lot of 30 bulbs which include 6 defectives, a sample of 4 bulbs is drawn
at random with replacement. Find the probability distribution of the number of
defective bulbs.\\
\solution
\input{ncert/9/3/18/main.tex}
 \item Suppose $X$ is a binomial distribution $B\left(6,\frac{1}{2}\right)$. Show that $X=3$ is the most likely outcome.
(Hint : $P(X=3)$ is the maximum among all $P(x_i),x_i=0,1,2,3,4,5,6$)\\
\solution
\input{ncert/9/3/19/main.tex}
\item A fair coin is tossed four times, and a person win Re $1$ for each head and lose Rs $1.5$ for each tail that turns up.\\
From the sample space calculate how many different amounts of money you can have after four tosses and the probability of having each of these amounts.
\solution
\item It is known that 10 $\%$ of certain articles manufactured are defective. What is the probability that in a random sample space of 12 such articles,9 are defective? \\
\solution
\input{ncert/9/3/21/main.tex}
\item An experiment succeeds twice as often as it fails. Find the probability that in the next
six trials, there will be atleast 4 successes.
\solution
\item A die is thrown 5 times. Find the probability that an odd number will come up exactly three times.
\solution
\input{ncert/9/3/23/main.tex}
\item Ten coins are tossed. What is the probability of getting atleast 8 heads?
\\
\solution 
\input{ncert/9/3/24/new.tex}
\item A factory produces bulbs. The probability that any one bulb is defective is $\frac{1}{50}$ and they are packed in boxes of 10. From a single box, find the probability that
\begin{enumerate}
    \item none of the bulb is defective 
    \item exactly two bulbs are defective 
    \item more than 8 bulbs are working properly
\end{enumerate}
\solution
\input{ncert/9/3/25/main.tex}
\item A lot of 100 watches is known to have 10 defective watches. If 8 watches are
selected (one by one with replacement) at random, what is the probability that
there will be at least one defective watch?
\solution
\input{ncert/9/3/26/main.tex}
\item The Probability of a man hitting  target is 0.25.He shoots 7 times. What is the probability of his hitting atleast twice?\\
\input{ncert/9/3/27/main.tex}
\item A person buys a lottery ticket in 50 lotteries in each of which his chance of winning a prize is $\frac{1}{100}$. What is the probability that he will win a prize
\begin{enumerate}[label=(\alph*)]
    \item  atleast once 
    \item exactly once 
    \item atleast twice ?
\end{enumerate}
\input{ncert/9/3/28/assignment8.tex}
\item The probability that a person is not a swimmer is 0.3. The probability that out of
5 persons 4 are swimmers is
\begin{enumerate}
    \item $\comb{5}{4}\brak{0.7}^4\brak{0.3}$
    \item $\comb{5}{1}\brak{0.7}\brak{0.3}^4$
    \item $\comb{5}{4}\brak{0.7}\brak{0.3}^4$
    \item $\brak{0.7}^4\brak{0.3}$
\end{enumerate}
\solution
\input{ncert/9/3/29/main.tex}
\item The probability of guessing correctly at least 8 out of 10 answers on a true-false
type examination is\\
\solution
\input{ncert/9/3/30/main.tex}
\item Eight coins are tossed together. The probability of getting exactly 3 heads is\\
\begin{enumerate}
    \item 
    $\frac{1}{256}$\\
    \item 
    $\frac{7}{32}$\\
    \item 
    $\frac{5}{32}$\\
    \item 
    $\frac{3}{32}$\\
\end{enumerate}
\input{ncert/9/3/31/main.tex}
\item If $X$ follows binomial distribution with parameters $n = 5$, $p$ and 
\begin{align}
    p_X(2) = 9p_X(3)
\end{align}
then $p$ is ?
\input{ncert/9/3/32(1)/main.tex}
\item A box has $100$ pens of which $10$ are defective. What is the probability that out of a sample of $5$ pens drawn one by one with replacement at most one is defective?
\begin{enumerate}[label=(\alph*)]
    \item $\brak{\frac{9}{10}}^5$
    \item $\frac{1}{2}\brak{\frac{9}{10}}^4$
    \item $\frac{1}{2}\brak{\frac{9}{10}}^5$
    \item $\frac{1}{2}\brak{\frac{9}{10}}^4 + \brak{\frac{9}{10}}^5$
\end{enumerate}
\solution
\input{ncert/9/3/33/main.tex}
%\end{enumerate}
