\begin{enumerate}[label=\thechapter.\arabic*,ref=\thechapter.\theenumi]
\item 
Find the mean number of heads in three tosses of a fair coin.
\\
\solution
\input{ncert/12/13/4/10/binom.tex}

\item Two dice are thrown simultaneously. If X denotes the number of sixes, find the
expectation of X.

\item Two numbers are selected at random (without replacement) from the first six
positive integers. Let X denote the larger of the two numbers obtained. Find
E(X).

\item Let X denote the sum of the numbers obtained when two fair dice are rolled.
Find the variance and standard deviation of X.

\item A class has 15 students whose ages are 14, 17, 15, 14, 21, 17, 19, 20, 16, 18, 20,
17, 16, 19 and 20 years. One student is selected in such a manner that each has
the same chance of being chosen and the age X of the selected student is
recorded. What is the probability distribution of the random variable X? Find
mean, variance and standard deviation of X.

\item In a meeting, 70% of the members favour and 30% oppose a certain proposal.
A member is selected at random and we take X = 0 if he opposed, and X = 1 if
he is in favour. Find E(X) and Var (X).\\

\item In a dice game, a player pays a stake of Re 1 for each throw of a die. She receives Rs 5 if the die shows a 3, Rs 2 if the die shows a 1 or 6, and nothing otherwise. What is the player’s expected profit per throw over a long series of throws?.\\
\solution
\input{exemplar/12/13/3/13/main.tex}

\item A die is thrown three times. Let X be 'the number of twos seen'. Find the expectation of X.\\
\solution
\input{exemplar/12/13/3/28/main.tex}

Choose the correct answer in each of the following:



\item The mean of the numbers obtained on throwing a die having written 1 on three
faces, 2 on two faces and 5 on one face is
\begin{enumerate}
\item 1
\item 2
\item 5
\item $\frac{8}{3}$

\end{enumerate}

\item Suppose that two cards are drawn at random from a deck of cards. Let X be the
number of aces obtained. Then the value of E(X) is
\begin{enumerate}

\item $\frac{37}{221}$
\item $\frac{5}{13}$
\item $\frac{1}{13}$
\item $\frac{2}{13}$

\end{enumerate}

\item Suppose $10000$ tickets are sold in a lottery each for Re. $1$. First prize is of Rs $3000$ and the second prize is of Rs $2000$. There are three third prizes of Rs. $500$ each. If you buy one ticket, what is your expectation.
\input{exemplar/12/13/3/15/main.tex}
\item Consider the probability distribution of a random variable X:
\begin{table}[H]
        \centering
        \input{exemplar/12/13/3/24/tables/tab.tex}
        \label{tab:exemplar/12/13/3/24}
    \end{table}
Calculate
\begin{enumerate}[label=(\roman*)]
\item var$\brak{X}$
\item var$\brak{\frac{X}{2}}$
\end{enumerate}
\solution
\input{exemplar/12/13/3/24/main.tex}
\item The random variable $X$ can take only the values $0,1,2$. Given that $\pr{X=0}=\pr{X=1}=p$ and that $E\brak{X^2} = E\brak{X}$, find the value of $p$.
\\
\input{exemplar/12/13/3/36/main.tex}
\item Find the variance of distribution.
\begin{table}[!ht]
	\input{exemplar/12/13/3/37/tables/table.tex}
\end{table}\\
\input{exemplar/12/13/3/37/main.tex}
\item Two cards are drawn successively without replacement from a well shuffled deck of cards. Find the mean and standard variation of random variable $X$ where $X$ is the number of aces.
\input{exemplar/12/13/3/53/main.tex}
\item The probability distribution of a discrete random variable X is given as under:
\begin{table}[ht]
    \centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
X & 1 & 2 & 4 & 2A & 3A & 5A  \\
\hline
\pr{X} & $\frac{1}{2}$ & $\frac{1}{5}$ & $\frac{3}{25}$ & $\frac{1}{10}$ & $\frac{1}{25}$ & $\frac{1}{25}$ \\
\hline
\end{tabular} 
\end{table}\\
Calculate:
\begin{enumerate}
\item The value of A if E(X) = 2.94
\item Variance of X.
\end{enumerate}
\input{exemplar/12/13/3/50/main.tex}
\item The probability distribution of a random variable $X$ is given as under:
\begin{align*}
    p_X(x) =
    \begin{cases}
        kx^2 &\text{for } x = 1,2,3\\
        2kx &\text{for } x = 4,5,6\\
        0 & \text{otherwise}
    \end{cases}
\end{align*}
where k is a constant. Calculate:
\begin{enumerate}
    \item $E\brak{X}$
    \item $E\brak{3X^2}$
    \item $\pr{X \geq 4}$
\end{enumerate}
\input{exemplar/12/13/3/51/main.tex}
\item Two probability distributions of the discrete random variable $X$ and $Y$ are given below.\\
\begin{table}[h!]
\begin{minipage}{0.45\linewidth}
 \begin{center}
  \caption{Table-1}
\begin{tabular}{|r|l|c|l|c|}
\hline
$X$ & 0 & 1 & 2 & 3\\
\hline
$P(X)$ & $\frac{1}{5}$ & $\frac{2}{5}$ & $\frac{1}{5}$ & $\frac{1}{5}$ \\
\hline
\end{tabular}
\end{center}
\end{minipage}
\end{table}

\begin{table}[h!]
\begin{minipage}{0.45\linewidth}
 \begin{center}
  \caption{Table-2}
\begin{tabular}{|r|l|c|l|c|}
\hline
$Y$ & 0 & 1 & 2 & 3\\
\hline
$P(Y)$ & $\frac{1}{5}$ & $\frac{3}{10}$ & $\frac{2}{5}$ & $\frac{1}{10}$ \\
\hline
\end{tabular}
\end{center}
\end{minipage}
\end{table}
Prove that $E\brak{Y^2}=2E\brak{X}$\\
\solution \\
\input{exemplar/12/13/3/30/main.tex}
\item For the following probability distribution determine standard deviation of the random variable $X$.
\begin{table}[h]
	\input{exemplar/12/13/3/26/tables/table.tex}
\end{table}\\
\input{exemplar/12/13/3/26/main.tex}
\item Let $X$ be a discrete random variable whose probability distribution is defined as follows:
\begin{align*}
\pr {X=x} =
\begin{cases} 
k(x+1) &,x =  1,2,3,4\\
2kx &, x = 5,6,7\\
0 &, otherwise
\end{cases}
\end{align*}
where $k$ is a constant. Calculate
\begin{enumerate}[label=(\roman*)]
\item the value of $k$
\item E\brak{X}
\item Standard deviation of $X$
\end{enumerate}
\solution
\\
\input{ncert/12/13/3/49/main.tex}
\item The probability distribution of a discrete random variable $X$ is given as under:
\begin{table}[!ht]
	\input{exemplar/12/13/3/50a/tables/spectral.tex}
\end{table}\\
Calculate:
\begin{enumerate}[label=\alph*)]
\item The value of $A$ if $E(X)$ =2.94
\item Variance of $X$.
\end{enumerate}
\input{exemplar/12/13/3/50a/main.tex}
\item A discrete random variable X has the probability distribution given as below:
\begin{table}[H]
\begin{tabular}{|c|c|c|c|c|}
\hline
X & 0.5 & 1 & 1.5 & 2 \\
\hline
P(X) & $k$ & $k^{2}$ & $2k^{2}$ & $k$ \\
\hline
\end{tabular}
\end{table}
\begin{enumerate}
\item{Find the value of $k$}
\item{Determine the mean of the distribution}
\end{enumerate}
\solution \\
\input{exemplar/12/13/3/10/main.tex}
\item There are 5 cards numbered 1 to 5, one number on one card. Two cards are drawn at random without replacement. Let X denote the sum of the numbers on two cards drawn. Find the mean and variance of X.
\input{exemplar/12/13/3/55/main.tex}
\item For the following probability distribution:
\begin{table}[!ht]
	\input{exemplar/12/13/3/88/tables/table1.tex}
\end{table}\\
$E\brak{X}$ is equal to:
\begin{enumerate}
	\item $0$ 
	\item $-1$ 
	\item $-2$ 
	\item $-1.8$ 
\end{enumerate}
\input{exemplar/12/13/3/88/main.tex}
\item If $A$, $B$ and $C$ are three independent events such that $\pr{A} = \pr{B} = \pr{C} = p$, then P(At least two of $A, B, C$ occur) = $3p^2-2p^3$\\
	\input{exemplar/12/13/3/103/main.tex}
\item For the following probability distribution
\begin{table}[!htb]
	\input{exemplar/12/13/3/89/tables/table.tex}
	\caption{Probability Distribution}
	\label{table1:ncert/12/13/3/89/}
\end{table}\\
E($X^{2}$)is equal to\\
(A)3  \qquad (B)5 \qquad (C)7 \qquad (D)10
\input{exemplar/12/13/3/89/main.tex}
\item A die is tossed twice. A ‘success’ is getting an even number on a toss. Find the variance of the number of successes.
	\\	\input{exemplar/12/13/3/54/main.tex}
 \item A biased die is such that $\pr{4} = \frac{1}{10}$ and other scores being equally likely. The die is tossed twice. If X is the 'number of fours seen', find the variance of the random variable X.\\
 \input{exemplar/12/13/3/27/main.tex}
 \item One million random numbers are generated from a statistically stationary process with a Gaussian distribution with mean zero and standard deviation $\sigma_0$.\\
The $\sigma_0$ is estimated by randomly drawing out 10,000 number of samples ($x_n$). The estimates $\hat{\sigma}^2_1$ and $\hat{\sigma}^2_2$ are computed in the following two ways:
\[
\hat{\sigma}^2_1 = \frac{1}{10000} \sum_{n=1}^{10000} x_n^2
\]
\[
\hat{\sigma}^2_2 = \frac{1}{9999} \sum_{n=1}^{10000} x_n^2
\]
Which of the following statements is true?
\begin{enumerate}
\item $E(\hat{\sigma}^2_2) = \sigma_0^2$ \label{eq:Option1}
\item $E(\hat{\sigma}_2) = \sigma_0$ \label{eq:Option2}
\item $E(\hat{\sigma}^2_1) = \sigma_0^2$ \label{eq:Option3}
\item $E(\hat{\sigma}_1) = E(\hat{\sigma}_2)$ \label{eq:Option4}
\end{enumerate} \hfill ( GATE EE 2023) \\
\solution
\input{gate/EE/2023/25/main.tex}
\item If X is the number of tails in three tosses of  coin, determine the standard deviation of X. \\
\input{exemplar/12/13/3/12/main.tex}
\item In a game, a man wins a rupee for a six and loses a rupee for any other number
when a fair die is thrown. The man decided to throw a die thrice but to quit as
and when he gets a six. Find the expected value of the amount he wins / loses.\\
\input{ncert/12/13/6/11/ncert.tex}
\end{enumerate}
